### 2017-11-27 paper/sections/2_parsplice-keyspace-analysis.tex
paper: addresses #26
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

The scalability experiment uses 1 splicer, 1 persistent database, 1 cache
process, and up to 2 workers. We scale up to 1024 tasks, which spans 32 nodes
and disable hyper-threading because we experience unacceptable variability in
performance. For the rest of the experiments, we use 8 nodes, 1 splicer, 1
persistent database, 1 cache process, 1 worker, and up to 256 tasks.  The
keyspace analysis that follows is for the cache on the worker node, which is
circled in Figure~\ref{fig:parsplice}.  The cache hierarchy is unmodified but
for the persistent database node, we replace BerkeleyDB on NFS with LevelDB on
Lustre. Original ParSplice experiments showed that BerkeleyDB's syncs caused
reads/writes to bottleneck on the persistent database. We also use Riak's
customized LevelDB\footnote{https://github.com/basho/leveldb} version, which
comes instrumented with its own set of performance counters.

>>>>

The scalability experiment uses 1 splicer, 1 persistent database, 1 cache
process, and up to 2 workers. We scale up to 1024 tasks, which spans 32 nodes
and disable hyper-threading because we experience unacceptable variability in
performance. For the rest of the experiments, we use 8 nodes, 1 splicer, 1
persistent database, 1 cache process, 1 worker, and up to 256 tasks.  The
keyspace analysis that follows is for the cache on the worker node, which is
circled in Figure~\ref{fig:parsplice}.

### 2017-11-27 paper/sections/3_methodology.tex
paper: addresses #26
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

% where policies are made
We link Mantle directly into the worker cache circled in red in
Figure~\ref{fig:parsplice}. We put the ``when" and ``how much" callbacks
alongside code that checks for memory pressure. It is executed right before the
worker processes incoming and outgoing put/get transactions to the cache. As
stated previously, we do not use the ``where" part of Mantle because we focus
on a single node, but this part of the API will be used when we move the caches
and storage nodes to a key-values store back-end that uses key load balancing and
repartitioning.

>>>>

% where policies are made
We link Mantle directly into the worker cache circled in red in
Figure~\ref{fig:parsplice}. We put the ``when" and ``how much" callbacks
alongside code that checks for memory pressure. It is executed right before the
worker processes incoming and outgoing put/get transactions to the cache. We
only do cache management once every second to avoid maintaining the cache for
every request. We expected to have to increase this polling interval to
accommodate more complex policies but even our most complicated policy in
Section~\S\ref{sec:dom-specific} had a negligible effect on performance when
executed every second (within the standard deviation for multiple runs when
compared against a policy that returns immediately). This may be because the
worker is not overloaded and the bottleneck is somewhere else in the system.
As stated previously, we do not use the ``where" part of Mantle because we
focus on a single node, but this part of the API will be used when we move the
caches and storage nodes to a key-values store back-end that uses key load
balancing and repartitioning.
